Einstein's gravity from a polynomial affine model

### 2015-11-04 AffGR-PRD.tex
Commiting the appendices
New version of Dimensional Analysis

%------------------
%--------- Definitions
%------------------
%% \input{Def-article.tex}
\usepackage{mathtools,amsmath,amssymb,amsfonts,dsfont,mathrsfs,amsthm}
\usepackage{graphicx}
\usepackage{centernot}
%% \usepackage{hyperref}
\usepackage{xcolor}
\usepackage{comment}
%% \hypersetup{linktocpage,colorlinks=true,urlcolor=blue!80!red,linkcolor=blue,citecolor=red}
%\usepackage{feynmf}
\usepackage{siunitx}
\usepackage{array}
%% \usepackage{ulem}
%\usepackage{tikz}
\usepackage{braket}
\usepackage{xparse}

@@

It is well-known that this system of equations can be obtained effectively from the Einstein--Hilbert action coupled minimally to a massless scalar field
\begin{equation}
  S_{\text{eff}} = \frac{1}{\alpha} \int \dn{4}{x} \sqrt{g} \left( R + 2 \Lambda - \frac{\alpha}{2} g^{\mu\nu} \pa{\mu}\phi \pa{\nu} \phi \right).
\end{equation}

@@

\input{DA.tex}

>>>>

%------------------
%--------- Definitions
%------------------
%% \input{Def-article.tex}
\usepackage{mathtools,amsmath,amssymb,amsfonts,dsfont,mathrsfs,amsthm}
\usepackage{graphicx}
\usepackage{centernot}
%% \usepackage{hyperref}
\usepackage{xcolor}
\usepackage{comment}
%% \hypersetup{linktocpage,colorlinks=true,urlcolor=blue!80!red,linkcolor=blue,citecolor=red}
%\usepackage{feynmf}
\usepackage{siunitx}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
%% \usepackage{ulem}
%\usepackage{tikz}
\usepackage{braket}
\usepackage{xparse}

@@

It is well-known that this system of equations can be obtained effectively from the Einstein--Hilbert action coupled minimally to a massless scalar field
\begin{equation}
  S_{\text{eff}} = \frac{1}{\alpha} \int \dn{4}{x} \sqrt{g} \left( R + 2 \Lambda - \frac{\alpha}{2} g^{\mu\nu} \pa{\mu}\phi \pa{\nu} \phi \right).
\end{equation}
We have show, so far, that our model of polynomial purely affine gravity is compatible with General Relativity in the sector of vanishing torsion, and in addition the compatibility can be extended to include the interaction with a free scalar field. The analysis of this coupled system could be enhanced to include a potential for the scalar field,

@@

\input{DA.tex}
\input{MS.tex}

### 2015-11-04 MS.tex
New version of Dimensional Analysis

Compact warped products of the form \mbox{$(M_1 \times M_2, f^{2} \cdot (g_1 \times g_2) )$,} where $M_1$ are two dimensional, $M_1$ has constant Gau\ss{}ian curvature, $K_1 < 0$, and $M_2$ is an Einstein manifold with scalar curvature $R_2 = - 2 K_1$ 
\hl{Working here}
%%\paragraph{}

>>>>

Compact warped products of the form \mbox{$(M_1 \times M_2, f^{2} \cdot (g_1 \times g_2) )$,} where $M_i$ are two two-dimensional manifolds, $M_1$ has constant Gau\ss{}ian curvature, $K_1 < 0$, and $M_2$ is an Einstein manifold with scalar curvature $R_2 = - 2 K_1$. The function $f: M_1 \to \R^+$ is a $C^\infty$ solution of 
\begin{equation*}
  \Lap f = c \, f^3 \text{ for } c > 0.
\end{equation*}

Many examples and explicit conditions of Riemannian metrics with harmonic curvature, and conditions for them to have parallel Ricci, can be found in Ref.~\cite{derdzinski1988riemannian}.

%%\paragraph{}
